% Converted from Microsoft Word to LaTeX
% by Chikrii Softlab Word2TeX converter (version 3.0)
% Copyright (C) 1999-2003 Chikrii Softlab. All rights reserved.
% http://www.chikrii.com
% mailto: info@chikrii.com
% License: infern0 / 

\documentclass{ctexart}
\usepackage{latexsym}
\usepackage[top=2.54cm,bottom=2.54cm,left=3.18cm,right=3.18cm]{geometry}
\setCJKmainfont[BoldFont=思源黑体 Medium,ItalicFont=方正楷体_GBK]{思源宋体}

\begin{document}

% You may use Title,Subject,Author,Manager,Company,Operator,
% Category,Comment,Hlinkbase document properties here
\title{}
\author{l allen}
\date{\today}
\maketitle

\begin{center}
secret, widely, since, produced, so, developed, way 
\end{center}

Wool is the hair that grows on sheep. Every year, over a million tons of 
wool is (1){\_}{\_}{\_}{\_}{\_}{\_}{\_}， 60{\%} of which goes into clothes. 
The most famous wool comes from Australian Merino sheep. Their wool is good 
for baby clothes, (2){\_}{\_}{\_}{\_}{\_}{\_}{\_} it is soft and keeps 
babies warm.

When wool is first cut from the sheep, it \textit{contains} (含有) a high level of oil, so 
before the wool is used, it must be cleaned. The simplest 
(3){\_}{\_}{\_}{\_}{\_}{\_}{\_}to do this is by putting the wool in warm 
water. The oil that \textit{is removed }(被去除)from the wool is (4){\_}{\_}{\_}{\_}{\_}{\_} 
used in products like hand creams.

Sheep were first used by humans several thousand years ago, but it is 
believed that they \textit{were raised} (被飼养)for meat rather than wool. When people (5) 
{\_}{\_}{\_}{\_}{\_} a way of cutting the wool from sheep, it became an 
important clothing material.

\begin{center}
interview, note, sends, hope, looking, arrive, no, chance, happy, ability, 
still, them 
\end{center}

Dear Vince,

I'm sorry I didn' t telephone you before I went back to Japan. I didn't get 
the (1){\_}{\_}{\_}{\_} to talk to you before I left, because everything 
happened suddenly. I (2){\_}{\_}{\_}{\_}{\_}{\_}{\_} that you are well and 
that everything is going well with your job.

When I was in England, I really missed my friends in Japan, so I was really 
(3){\_}{\_}{\_}{\_}to get back here, to see everyone again and catch up with 
the news. Do you remember Masako? We often talk about you, and she 
(4){\_}{\_}{\_}{\_}{\_}{\_}{\_}her best wishes to you. Well, I have had 
letters from some of our friends in England. Do you still see 
(5){\_}{\_}{\_}{\_}{\_}?

I've been looking for a job and I've written aboutthirty letters of 
\textit{applications}(求职信)，but so far I' ve gotten (6){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_} 
replies. However, two days ago my father said that a friend of his was 
(7){\_}{\_}{\_}{\_}{\_} for someone who speaks English to work for two 
months as a \textit{receptionist}(接待员)in his \textit{company's} (公司的)office in London. Yesterday, I went for 
the (8){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}and I got the job, so in 
three weeks I'll be back in England!

Do you (9){\_}{\_}{\_}{\_}{\_}{\_}{\_}have the same phone number? I'll give 
you a call when I (10){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_} perhaps we could 
meet up and go out for a meal or something like that. It would be great to 
see you again.

\begin{flushright}
Yours，
\end{flushright}

\begin{flushright}
Chiyo
\end{flushright}

\begin{center}
visit, dare, problem, although, how, background, could, absent, sick, 
planned, proud, with 
\end{center}

Picture this scene. You wake up on a school morning, and you know you're 
(1){\_}{\_}{\_}{\_}{\_}{\_}{\_} Maybe your throat is sore. Maybe your head 
hurts. Whatever the (2){\_}{\_}{\_}{\_}{\_}{\_}{\_}is, your mom or your dad 
sends you back to bed to rest. This happens to every kid once in a while, 
right?

Wrong, And the living \textit{proof} (证据)is eighteen-year-old Travis Schmidt. From his 
first day of \textit{kindergarden}(幼儿园)to his last day of high school, Travis never stayed 
home sick. At first，Travis didn't think too much about never being 
(3){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}. But then he reached third grade 
(4){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}perfect \textit{attendance }(出勤率). At that point, 
Travis decided to see how long he (5){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}keep it 
up.

So (6){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_} did Travis successfully keep 13 years 
of perfect attendance? In the first place, he's a very healthy kid. 
(7){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_} he got colds like everyone else, Travis 
never felt sick enough to stay home. Travis also 
(8){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_} \textit{ahead} (提前地) For example, he knew he' d 
probably get \textit{chicken pox}(水痘)sooner or later. So when a friend caught chicken pox one 
summer, Travis made sure to (9){\_}{\_}{\_}{\_}{\_}{\_}{\_}him. A few days 
later, he was covered with poxes. But he had quite a lot of time to get 
better before school started in the fall.

Travis is (10){\_}{\_}{\_}{\_}{\_}{\_}{\_} of his record. ``l may not be the 
smartest or the coolest. But I'm always there.'' he says.

\begin{center}
sleeping, promised, him, hardly, nervous, water,happening, mentioned, tired, 
arrived, already, wanted 
\end{center}

Barry and Selma were very worried. Where was their ten-year-old son Sean, 
and what was (1){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_} to him? They only 
arrived at their apartment two hours earlier, and the holiday was 
(2){\_}{\_}{\_}{\_}{\_}{\_}{\_}a disaster (灾祸).

Everything started quite well. The whole family -- Bany, Selma, and their 
children Sean and Lily (3){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}a seaside 
holiday，so they \textit{rented} (租)an apartment on a quiet beach in Spain. They were all 
really excited when they (4){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}, so they 
dropped off their things in the apartment and all went straight down to the 
beach.

While Sean and Lily were playing in the (5){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}, 
Barry and Selma were talking about their holiday plans. After a swim, Sean 
said he wanted to go fishing at the other end of the beach. Barry and Selma 
told (6){\_}{\_}{\_}{\_}{\_}{\_}{\_}to come back before 8:00, but by 8:30, 
Sean still hadn , t returned. They went to look for him, but nobody saw the 
boy. Everyone got very (7){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}, and decided to 
go back to the apartment to call the police. But shortly after Barry 
\textit{dialed} (拨号)the number they got a big surprise.

The surprise was that Sean was (8){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}in his 
bedroom. The boy had \textit{misunderstood} (误解) his parents' instructions to ``come back''，and 
went back to the apartment by himself. He was 
(9){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_} after fishing, so he fell 
asleep. He opened his eyes and

couldn, t understand why everyone was so worried. But when the police 
arrived five minutes later, he (10){\_}{\_}{\_}{\_}{\_}{\_}{\_}that he would 
not disappear again!

\begin{center}
laughing, bored, serious, its, car, patient, decided, 
nearly，together，ended，across，saw 
\end{center}

Two years ago, I went to Perth, Australia for a meeting with my partner, 
Chris. We decided to drive across the country to Brisbane after the meeting 
(1){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}. The drive was going to take four days 
and most of it was (2){\_}{\_}{\_}{\_}{\_}the desert. 

The first day was fun. By the third day of driving in the seemingly endless 
desert, we began to get (3){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}. We had been 
quiet for a few hours when in the \textit{distance }(远方)Chris found some 
\textit{kangaroos}(袋鼠).We were both excited and (4){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_} 
to get a closer look. Chris \textit{accelerated} (加速) to catch up with the kangaroos. We got 
closer and closer and suddenly we heard a loud BANG!

Chris stopped the (5){\_}{\_}{\_}{\_}{\_}{\_}{\_} and we got out. Behind the 
car was a large kangaroo lying on the ground quiet. Chris went over to the 
kangaroo and put his baseball cap on (6){\_}{\_}{\_}{\_}{\_}{\_} head. He 
took off his jacket and put it on the kangaroo. Then, he put his arm

around the kangaroo and told me to take a photo of them 
(7){\_}{\_}{\_}{\_}{\_}{\_}{\_}{\_}. I was still in shock, but I took out my 
camera. While I was \textit{focusing} (调节焦距) the camera, I 
(8){\_}{\_}{\_}{\_}{\_}{\_}{\_}the kangaroo move. It suddenly woke up, 
looked at Chris, and \textit{hopped away} (跳走) into the distance before we could do anything.

I started laughing but Chris looked very (9){\_}{\_}{\_}{\_}{\_}{\_}{\_}. He 
said his wallet was in the jacket. I started laughing even harder. I stopped 
(10){\_}{\_}{\_}{\_}, however, when he said that our car keys were also in 
the jacket!

\end{document}
