% Converted from Microsoft Word to LaTeX
% by Chikrii Softlab Word2TeX converter (version 3.0)
% Copyright (C) 1999-2003 Chikrii Softlab. All rights reserved.
% http://www.chikrii.com
% mailto: info@chikrii.com
% License: infern0 / 

\documentclass{article}
\usepackage{latexsym,xeCJK}
\usepackage[top=2.54cm,bottom=2.54cm,left=3.18cm,right=3.18cm]{geometry}
\setCJKmainfont{方正楷体_GBK}
\setmainfont{Georgia}
\newcommand{\kong}{\rule{4em}{0.5pt} }
\begin{document}


\begin{center}
\fbox{secret, widely, since, produced, so, developed, way }
\end{center}

Wool is the hair that grows on sheep. Every year, over a million tons of 
wool is (1)\kong ， 60{\%} of which goes into clothes. 
The most famous wool comes from Australian Merino sheep. Their wool is good 
for baby clothes, (2)\kong \ it is soft and keeps 
babies warm.

When wool is first cut from the sheep, it \textit{contains}\/(含有) a high level of oil, so 
before the wool is used, it must be cleaned. The simplest 
(3)\kong to do this is by putting the wool in warm 
water. The oil that \textit{is removed}\/(被去除) from the wool is (4)\kong  
used in products like hand creams.

Sheep were first used by humans several thousand years ago, but it is 
believed that they \textit{were raised}\/(被飼养) for meat rather than wool. When people (5) 
\kong  a way of cutting the wool from sheep, it became an 
important clothing material.

\begin{center}
\fbox{interview, note, sends, hope, looking, arrive, no, chance, happy, ability, still, them }
\end{center}

Dear Vince,

I'm sorry I didn' t telephone you before I went back to Japan. I didn't get 
the (1)\kong  to talk to you before I left, because everything 
happened suddenly. I (2)\kong  that you are well and 
that everything is going well with your job.

When I was in England, I really missed my friends in Japan, so I was really 
(3)\kong to get back here, to see everyone again and catch up with 
the news. Do you remember Masako? We often talk about you, and she 
(4)\kong her best wishes to you. Well, I have had 
letters from some of our friends in England. Do you still see 
(5)\kong ?

I've been looking for a job and I've written aboutthirty letters of 
\textit{applications}\/(求职信)， but so far I' ve gotten (6)\kong  
replies. However, two days ago my father said that a friend of his was 
(7)\kong  for someone who speaks English to work for two 
months as a \textit{receptionist}\/(接待员) in his \textit{company's} (公司的)office in London. Yesterday, I went for 
the (8)\kong and I got the job, so in 
three weeks I'll be back in England!

Do you (9)\kong have the same phone number? I'll give 
you a call when I (10)\kong  perhaps we could 
meet up and go out for a meal or something like that. It would be great to 
see you again.

\begin{flushright}
Yours，

Chiyo
\end{flushright}

\begin{center}
\fbox{visit, dare, problem, although, how, background, could, absent, sick, planned, proud, with }
\end{center}

Picture this scene. You wake up on a school morning, and you know you're 
(1)\kong  Maybe your throat is sore. Maybe your head 
hurts. Whatever the (2)\kong is, your mom or your dad 
sends you back to bed to rest. This happens to every kid once in a while, 
right?

Wrong, And the living \textit{proof}\/(证据) is eighteen-year-old Travis Schmidt. From his 
first day of \textit{kindergarden}\/(幼儿园) to his last day of high school, Travis never stayed 
home sick. At first，Travis didn't think too much about never being 
(3)\kong . But then he reached third grade 
(4)\kong perfect \textit{attendance}\/(出勤率). At that point, 
Travis decided to see how long he (5)\kong keep it 
up.

So (6)\kong  did Travis successfully keep 13 years 
of perfect attendance? In the first place, he's a very healthy kid. 
(7)\kong  he got colds like everyone else, Travis 
never felt sick enough to stay home. Travis also 
(8)\kong  \textit{ahead}\/(提前地) For example, he knew he' d 
probably get \textit{chicken pox}\/(水痘) sooner or later. So when a friend caught chicken pox one 
summer, Travis made sure to (9)\kong him. A few days 
later, he was covered with poxes. But he had quite a lot of time to get 
better before school started in the fall.

Travis is (10)\kong  of his record. ``l may not be the 
smartest or the coolest. But I'm always there.'' he says.

\begin{center}
\fbox{\parbox{\linewidth}{\centering sleeping, promised, him, hardly, nervous, water,happening, mentioned, tired, arrived, already, wanted}}
\end{center}

Barry and Selma were very worried. Where was their ten-year-old son Sean, 
and what was (1)\kong  to him? They only 
arrived at their apartment two hours earlier, and the holiday was 
(2)\kong a \textit{disaster}\/(灾祸).

Everything started quite well. The whole family -- Bany, Selma, and their 
children Sean and Lily (3)\kong a seaside 
holiday，so they \textit{rented}\/(租) an apartment on a quiet beach in Spain. They were all 
really excited when they (4)\kong , so they 
dropped off their things in the apartment and all went straight down to the 
beach.

While Sean and Lily were playing in the (5)\kong , 
Barry and Selma were talking about their holiday plans. After a swim, Sean 
said he wanted to go fishing at the other end of the beach. Barry and Selma 
told (6)\kong to come back before 8:00, but by 8:30, 
Sean still hadn't returned. They went to look for him, but nobody saw the 
boy. Everyone got very (7)\kong , and decided to 
go back to the apartment to call the police. But shortly after Barry 
\textit{dialed}\/(拨号) the number they got a big surprise.

The surprise was that Sean was (8)\kong in his 
bedroom. The boy had \textit{misunderstood}\/(误解) his parents' instructions to ``come back''，and 
went back to the apartment by himself. He was 
(9)\kong  after fishing, so he fell 
asleep. He opened his eyes and

couldn, t understand why everyone was so worried. But when the police 
arrived five minutes later, he (10)\kong that he would 
not disappear again!

\begin{center}
\fbox{laughing, bored, serious, its, car, patient, decided, nearly，together，ended，across，saw }
\end{center}

Two years ago, I went to Perth, Australia for a meeting with my partner, 
Chris. We decided to drive across the country to Brisbane after the meeting 
(1)\kong . The drive was going to take four days 
and most of it was (2)\kong the desert. 

The first day was fun. By the third day of driving in the seemingly endless 
desert, we began to get (3)\kong . We had been 
quiet for a few hours when in the \textit{distance}\/(远方) Chris found some 
\textit{kangaroos} (袋鼠).We were both excited and (4)\kong  
to get a closer look. Chris \textit{accelerated}\/(加速) to catch up with the kangaroos. We got 
closer and closer and suddenly we heard a loud BANG!

Chris stopped the (5)\kong  and we got out. Behind the 
car was a large kangaroo lying on the ground quiet. Chris went over to the 
kangaroo and put his baseball cap on (6)\kong  head. He 
took off his jacket and put it on the kangaroo. Then, he put his arm

around the kangaroo and told me to take a photo of them 
(7)\kong . I was still in shock, but I took out my 
camera. While I was \textit{focusing}\/(对焦) the camera, I 
(8)\kong the kangaroo move. It suddenly woke up, 
looked at Chris, and \textit{hopped away}\/(跳走) into the distance before we could do anything.

I started laughing but Chris looked very (9)\kong . He 
said his wallet was in the jacket. I started laughing even harder. I stopped 
(10)\kong , however, when he said that our car keys were also in 
the jacket!

\begin{center}
\fbox{another, even, when, yes, homework, why, forgot, with, learn, helped, wanted, gave}
\end{center}

Susan was a woman who hated animals very much. She never (1)\kong to keep any pets at home. To her, all pets were very dirty and boring. Susan could never understand (2)\kong people would like to have pets in the house. “It is so stupid!” she always said.

Last month Susan's daughter, Penny, came home from school (3)\kong a mouse in a box. Susan was very angry. But Penny said that it was her (4)\kong. Her teacher asked each student to take care of an animal and (5)\kong to get along with it. Susan had to say (6)\kong .

It was fun for Penny at the very beginning, but then she got quite lazy and (7)\kong to do her homework. It became Susan’s homework. She (8)\kong it food and water every day and found that the mouse was in fact not dirty. She (9)\kong talked to it! It was not boring or stupid! Now Susan is having a good time with “her” mouse. She named it Nini. And she is going to buy (10)\kong one to make a pair.

\begin{center}
\fbox{invent, doubt, mention, website, all of a sudden}
\end{center}

It is often difficult to decide on the inventor of certain inventions. This is because sometimes a few people may (1)\kong things which are nearly the same. It’s hard to tell who came up with the
idea first. Some inventions can also lead to other inventions (2)\kong. So some people (3)\kong whether the inventor came up with the idea himself or herself. They think that the inventor used someone else s idea to create his or her invention. That is why books or (4)\kong usually (5) \kong more than one inventor when giving information about inventions.

\end{document}
